\speculake: Hiding Malware in Speculative Execution

### 2018-08-06 paper/introduction.tex
add paragraph about trigger inputs to intro

While it's possible for the trigger and payload programs to be bundled in a
single program, an analyst aware of \speculake could easily find the speculative
gadget in the payload program based on the jump pattern in the trigger program.
However, if the trigger and payload are kept separate, the analyst has a much
harder job and must identify both.
Moreover, it is possible that the trigger program be a
seemingly-unrelated benign program already on the victim's computer. We
investigate using the OpenSSL library as a benign trigger
program in Section~\ref{subsec:openssl}. If the trigger program is another benign
program on the system, the analyst has the difficult task of identifying which
program, library, or even operating system component is responsible for training
the CPU's branch predictor, and finding the specific set of jumps that occur at
runtime. To make matters worse, the payload program can include dummy jump
patterns that are effectively dead ends for the analyst, as they do not
ultimately call the hidden speculative gadget.

>>>>

While it's possible for the trigger and payload programs to be bundled in a
single program, an analyst aware of \speculake could easily find the speculative
gadget in the payload program based on the jump pattern in the trigger program.
However, if the trigger and payload are kept separate, the analyst has a much
harder job and must identify both.

Moreover, it is possible that the trigger program be a
seemingly-unrelated benign program already on the victim's computer. We
show this using the OpenSSL library as a benign trigger
program in Section~\ref{subsec:openssl}. If the trigger program is another benign
program on the system, the analyst has the difficult task of identifying which
program, library, or even operating system component is responsible for training
the CPU's branch predictor, and finding the specific set of jumps that occur at
runtime. To make matters worse, the payload program can include dummy jump
patterns that are effectively dead ends for the analyst, as they do not
ultimately call the hidden speculative gadget.

We also show it is possible to obviate the trigger program entirely, and
instead use \emph{trigger inputs}, which are attacker-provided data inputs to
the payload that cause the CPU to speculatively execute
at the attacker's chosen address. Unlike traditional malware input triggers, these inputs
cannot be inferred from the payload binary using static analysis or symbolic
execution, as the logic these triggers activate happens speculatively in the
CPU, which existing analysis tools do not model. We describe this technique in
more detail in Section~\ref{subsec:spec-buffer-overflow}.
